---
title: "Nightly EDAS Pin updates"
author: "Emma Jones"
date: "3/2/2021"
output: html_document
resource_files:
- config.yml
---


This nightly pin update is only run seasonally during assessment periods. Typically, the EDAS data is analyzed and make available weekly to biologists; however, during the period leading up to an assessment, we need the biologists to be able to enter data and analyze the data as soon as possible (the next day due to ODS refresh rate).

This pin is scheduled to run nightly on the Connect platform for the critical period of time ~February-June during an assessment year.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

httr::set_config(httr::config(ssl_verifypeer = FALSE, ssl_verifyhost = FALSE))

library(tidyverse)
library(sf)
library(pool)
library(geojsonsf)
library(DBI)
library(pins)
library(config)
library(lubridate)
library(dbplyr)

# get configuration settings
conn <- config::get("connectionSettings")

# use API key to register board
board_register_rsconnect(key = conn$CONNECT_API_KEY,  #Sys.getenv("CONNECT_API_KEY"),
                          server = conn$CONNECT_SERVER)#Sys.getenv("CONNECT_SERVER"))

source('helperFunctions/VSCI_metrics_GENUS.R')
source('helperFunctions/VCPMI_metrics_GENUS.R')


```
 
```{r connect to ODS}
## For testing: connect to ODS production
# pool <- dbPool(
#   drv = odbc::odbc(),
#   Driver = "ODBC Driver 11 for SQL Server",#Driver = "SQL Server Native Client 11.0",
#   Server= "DEQ-SQLODS-PROD,50000",
#   dbname = "ODS",
#   trusted_connection = "yes"
# )

# establish db connection on server
pool <- dbPool(
  drv = odbc::odbc(),
  Driver = "SQLServer",   # note the LACK OF space between SQL and Server ( how RStudio named driver)
  Server = "DEQ-SQLODS-PROD,50000",
  dbname = "ODS",
  UID = conn$UID_prod,# use config file         #Sys.getenv("userid"), # plug this in on server
  PWD = conn$PWD_prod, # use config file         #Sys.getenv("pwd") # plug this in on server
  trusted_connection = "yes"
)

# con <- dbConnect(odbc::odbc(),.connection_string = 'driver={SQL Server Native Client 11.0};server={DEQ-SQLODS-PROD,50000};database={ODS};trusted_connection=yes')

```



Pull Genus Master Taxa list.

```{r masterTaxaGenus}
masterTaxaGenus <- pool %>% tbl(in_schema("wqm",  "Edas_Benthic_Master_Taxa_View")) %>%
  as_tibble() %>%
  # make columns match expected format
  rename('Phylum' = 'PHYLUM_NAME',
         'Class' = 'CLASS_NAME',
         'Subclass' = 'SUBCLASS_NAME',
         'Order' = 'ORDER_NAME',
         'Suborder' = 'SUBORDER_NAME',
         'Superfamily' = 'SUPERFAMILY_NAME',
         'Family' = 'FAMILY_NAME',
         'Subfamily' = 'SUBFAMILY_NAME',
         'Tribe' = 'TRIBE_NAME',
          'Genus' = 'GENUS_NAME',
          'Species' = 'SPECIES_NAME',
          "Final VA Family ID" =  "WBMT_FINAL_FAMILY_ID",
          "FinalID" = "WBMT_FINAL_ID",
          "TolVal" = "WBMT_TOLERANCE_VALUE",
          "FFG" =   "FEEDING_GROUP", 
          "Habit" = "HABIT", 
          "FamFFG" =  "FAMILY_FEEDING_GROUP",
          "FamTolVal" = "WBMT_FAM_TOLERANCE_VALUE",
          "FamHabit" ="FAMILY_HABIT") %>% 
  dplyr::select(Phylum, Class, Subclass, Order, Suborder, Superfamily, Family, Subfamily, Tribe, 
                Genus, Species, `Final VA Family ID`, FinalID, TolVal, FFG, 
                Habit, FamFFG, FamTolVal, FamHabit) # keep EDAS Master Taxa list names
```

Pull Benthics 

```{r benthics}
benthics <- pool %>% tbl(in_schema("wqm",  "Edas_Benthic_View")) %>%
        as_tibble() %>%
        rename( "StationID" = "STA_ID",
                "BenSampID"  = "WBS_SAMP_ID",
                "RepNum" = "WBS_REP_NUM",
                "FinalID" = "WBMT_FINAL_ID",
                "Individuals" = "WBE_INDIVIDUALS",
                "ID Comments" = "WBE_COMMENT",
                "Entered By" = "WBE_INSERTED_BY", # not in EDAS table but good info
                "Taxonomist" = "TAXONOMIST_NAME",  # not in EDAS table but good info
                "Entered Date" = "WBE_INSERTED_DATE") %>%
        mutate(`Excluded Taxa` = ifelse(WBE_EXCLUDED_TAXA_YN == "Y", -1, 0)) %>%
        dplyr::select(StationID, BenSampID, RepNum, FinalID, Individuals, `Excluded Taxa`, `ID Comments`, Taxonomist, `Entered By`, `Entered Date`)
```

Pull BenSamps 

```{r benSamps}
benSamps <- pool %>% tbl(in_schema("wqm",  "Edas_Benthic_Sample_View")) %>%
        as_tibble() %>%
        # fix names
        rename( "StationID" = "STA_ID",
                "BenSampID"  = "WBS_SAMP_ID",
                "RepNum" = "WBS_REP_NUM",
                "Sample Comments" = "WBS_COMMENT",
                "Entered By" = "WBS_INSERTED_BY", # not in EDAS table but good info
                "Collected By" = "COLLECTOR_NAME",  # not in EDAS table but good info
                "Entered Date" = "WBS_INSERTED_DATE",
                "Gradient" = "WBCM_DESCRIPTION",
                "Taxonomist" = "TAXONOMIST_NAME",  # not in EDAS table but good info
                "Target Count" = "WBS_TARGET_COUNT",
                "Field Team" = "WBS_FIELD_TEAM",
                "Collection Date" = "FDT_DATE_TIME") %>%
        # Add sample season 
        mutate(monthday = as.numeric(paste0(sprintf("%02d",month(`Collection Date`)),
                                            sprintf("%02d",day(`Collection Date`)))),
               Season = case_when(monthday >= 0215 & monthday <= 0615 ~ 'Spring',
                                  monthday >= 0815 & monthday <= 1215 ~ 'Fall',
                                  TRUE ~ as.character("Outside Sample Window"))) %>%
        dplyr::select(StationID, BenSampID, RepNum, `Collection Date`, `Sample Comments`, `Collected By`, `Field Team`, `Entered By`,
                      Taxonomist, `Entered Date`, Gradient, `Target Count`, Season)

```

After we bring in WQM_Stations (CEDS) and WQM_Stations_Full (REST) we will improve this BenSamps dataset with ecoregion and assessment region information in a separate pin.


Pull HabSamps

```{r habSamps}
habSamps <- pool %>% tbl(in_schema("wqm",  "Edas_Habitat_Sample_View")) %>%
        as_tibble() %>%
        rename("StationID" = "STA_ID",
               "HabSampID" = "WHS_SAMP_ID",
               "Entered Date" = "WHS_INSERTED_DATE",
               "Entered By" = "WHS_INSERTED_BY",
               "Field Team" = "WHS_FIELD_TEAM",
               "HabSample Comment" = "WHS_COMMENT",
               "Gradient" = "WSGC_DESCRIPTION",
               "Collection Date" = "FDT_DATE_TIME") %>%
        # Add sample season 
        mutate(monthday = as.numeric(paste0(sprintf("%02d",month(`Collection Date`)),
                                            sprintf("%02d",day(`Collection Date`)))),
               Season = case_when(monthday >= 0215 & monthday <= 0615 ~ 'Spring',
                                  monthday >= 0815 & monthday <= 1215 ~ 'Fall',
                                  TRUE ~ as.character("Outside Sample Window"))) %>%
        dplyr::select(HabSampID, StationID, `Collection Date`, `Entered By`, `Entered Date`, `Field Team`, `HabSample Comment`, Gradient, Season)
      
```

Pull HabValues

```{r habValues}
habValues <- pool %>% tbl(in_schema("wqm",  "Edas_Habitat_Values_View")) %>%
        as_tibble() %>%
        rename("HabSampID" = "WHS_SAMP_ID",
               "HabParameter" = "WHVP_CODE",
               "HabParameterDescription" = "WHVP_DESCRIPTION",
               "HabValue" = "WHV_HAB_VALUE",
               "HabValue Comment" = "WHV_COMMENT") %>%
        dplyr::select(HabSampID, HabParameter, HabParameterDescription, HabValue, `HabValue Comment`)
```


Pull WQM_Stations_View.

```{r WQM_Stations_View}
WQM_Stations_View <- pool %>% tbl(in_schema("wqm",  "Wqm_Stations_View")) %>%  
  as_tibble()
```


Pull WQM_Sta_GIS_View.

```{r WQM_Sta_GIS_View}
WQM_Sta_GIS_View <- pool %>% tbl(in_schema("wqm",  "Wqm_Sta_GIS_View")) %>%  
  as_tibble()
```


Pull HabObs

```{r habObs}
habObs <- pool %>% tbl(in_schema("wqm",  "Edas_Habitat_Observations_View")) %>%
        as_tibble() %>%
        rename("HabSampID" = "WHS_SAMP_ID",
               "ObsParameter" = "WOBP_CODE",
               "ObsParameterDescription" = "WOBP_DESCRIPTION",
               "ObsValue" = "WOB_OBS_VALUE") %>%
        dplyr::select(HabSampID, ObsParameter, ObsParameterDescription, ObsValue) 
```

Make Total Habitat pin

```{r totHab}
totalHabitatScore <- habValues %>% 
  group_by(HabSampID) %>% 
  summarise(`Total Habitat Score` = sum(HabValue, na.rm = T)) %>% 
  left_join(habSamps, by = 'HabSampID') %>% 
  dplyr::select(StationID, `Collection Date`, HabSampID, `Field Team`, `HabSample Comment`, Gradient, Season, `Total Habitat Score`)
```

Create a BenSampsStations dataset with ecoregion and assessment region information
```{r ecoregion assessment}
#Bring in extra large ecoregion and assessment region files. By extra large we mean that they are continuous outside the state boundary such that stations that fall outside the state are not removed when spatially intersected
ecoregionLarge <- st_read('data/GIS/VA_level3ecoregion_WGS84.shp')
ecoregion4Large <- st_read('data/GIS/VA_level4ecoregion_WGS84.shp')
county <- st_read('data/GIS/VACountyBoundaries.shp')
#assessmentRegionLarge <- st_read('data/GIS/AssessmentRegions_buffer.shp')
```

How I made the unrestrictedAssessmentRegionVAHU6Subbasin layer:

```{r unrestrictedAssessmentRegionVAHU6Subbasin}
vahu6 <- st_read('data/GIS/VA_SUBWATERSHED_6TH_ORDER_STG.shp') # this version of vahu6 layer goes outside state boundary
subbasinConversion <- read_csv('data/subbasinToVAHU6conversion.csv')
unrestrictedAssessmentRegionVAHU6Subbasin <- left_join(vahu6, subbasinConversion, by = c('VAHU6', 'VAHU5'))
```

Make a WQM_Stations_Spatial dataset that has spatially derived ecoregion, county, subbasin, and assessment info.

```{r WQM_Stations_Spatial}
# bring in what already has data
WQM_Stations_Spatial_pin <- pin_get('ejones/WQM-Stations-Spatial') 

# identify any new sites that have been added to CEDS since the last analysis or stations that have been changed in CEDS since the last analysis!
WQM_Stations_Spatial1 <- filter(WQM_Sta_GIS_View, ! Station_Id %in% WQM_Stations_Spatial_pin$StationID | 
                                  as.Date(Changed_Date) > Sys.Date()-7) %>%
  #WQM_Sta_GIS_View %>% # For when running a big new analysis where all data needs it
  distinct(Station_Id, .keep_all = T) %>% # first makes sure only 1 record per station
  filter(!is.na(Latitude) | !is.na(Longitude)) %>% # make sure all stations have coordinates
  dplyr::select(StationID = Station_Id, Latitude, Longitude) %>% 
  left_join(dplyr::select(WQM_Stations_View, Sta_Id, Sta_Desc), by = c('StationID' = 'Sta_Id')) %>%   # add Station description info
  distinct(StationID, .keep_all = T) %>% # again makes sure only 1 record per station
  st_as_sf(coords = c("Longitude", "Latitude"),  # make spatial layer using these columns
           remove = F, # don't remove these lat/lon cols from df
           crs = 4326) 

# # Add Level 3 Ecoregion Info
# WQM_Stations_SpatialEco <- filter(WQM_Stations_Spatial1, is.na(US_L3CODE)) %>%
#   st_intersection(#WQM_Stations_Spatial1, 
#     dplyr::select(ecoregionLarge, US_L3CODE, US_L3NAME)) %>%st_drop_geometry()

# Add Level 3 and 4 Ecoregion Info
WQM_Stations_SpatialEco <- #filter(WQM_Stations_Spatial1, is.na(US_L3CODE)) %>%
  st_intersection(WQM_Stations_Spatial1, dplyr::select(ecoregion4Large, US_L3CODE, US_L3NAME, US_L4CODE, US_L4NAME )) %>%st_drop_geometry()

# CountyCity Name info
WQM_Stations_SpatialCounty <- st_intersection(WQM_Stations_Spatial1, dplyr::select(county, CountyCityName = NAME, FIPS)) %>%st_drop_geometry()

# Add Assessment and Basin Info
WQM_Stations_SpatialAssess <- st_intersection(WQM_Stations_Spatial1,unrestrictedAssessmentRegionVAHU6Subbasin) %>% #assessmentRegionLarge) %>%
  distinct(StationID, .keep_all = T) %>% st_drop_geometry() 
#  mutate(ASSESS_REG = ASSESS_REG.1) %>% 
#  dplyr::select(-c(OBJECTID:HUMOD, OBJECTID_1, ASSESS_REG.1))%>% st_drop_geometry()

WQM_Stations_Spatial2 <- full_join(dplyr::select(WQM_Stations_SpatialEco, StationID:US_L4NAME),
                                        dplyr::select(WQM_Stations_SpatialAssess, StationID, VAHU6, ASSESS_REG:Basin_Code ),
                                        by='StationID') %>% 
  full_join(dplyr::select(WQM_Stations_SpatialCounty, StationID, CountyCityName, FIPS),
            by = 'StationID')

# Fix any sites that are missing lat/lng after combining eco and assessment info (missing coords from assessment step)
WQM_Stations_Spatial2fix <- filter(WQM_Stations_Spatial2, is.na(Latitude) | is.na(Longitude)) %>% 
  left_join(WQM_Stations_Spatial1 %>% st_drop_geometry(), by = 'StationID') %>% 
  dplyr::select(StationID, Latitude = `Latitude.y`, Longitude = `Longitude.y`, Sta_Desc = `Sta_Desc.y`, 
                US_L3CODE:Basin_Code)

WQM_Stations_Spatial3 <- bind_rows(filter(WQM_Stations_Spatial2, !StationID %in% WQM_Stations_Spatial2fix$StationID),
                                   WQM_Stations_Spatial2fix)

WQM_Stations_Spatial <- bind_rows(WQM_Stations_Spatial_pin, WQM_Stations_Spatial3)

```

Make a benSampsStations dataset that has spatially derived ecoregion, subbasin, and assessment info.

```{r benSampsStations}
benSampsStations1 <- benSamps %>%
  group_by(StationID) %>%
  mutate(`Total Station Visits (Not Sample Reps)` = n()) %>%
  ungroup() %>%
  distinct(StationID, .keep_all = T) %>%
  left_join(dplyr::select(WQM_Sta_GIS_View, Station_Id, Latitude, Longitude), by = c('StationID' = 'Station_Id')) %>%
  # add Station description info
  left_join(dplyr::select(WQM_Stations_View, Sta_Id, Sta_Desc), by = c('StationID' = 'Sta_Id')) %>%
  dplyr::select(StationID, Sta_Desc, `Total Station Visits (Not Sample Reps)`, Latitude, Longitude) %>%
  #pull this where readily available to save time
  left_join(dplyr::select(WQM_Stations_Spatial,StationID, US_L3CODE:US_L4NAME),
            by ='StationID') %>%
  # left_join(dplyr::select(WQM_Station_Full, WQM_STA_ID, US_L3CODE = EPA_ECO_US_L3CODE, US_L3NAME = EPA_ECO_US_L3NAME),
  #           by =c('StationID'= 'WQM_STA_ID')) %>%
  filter(!is.na(Latitude) | !is.na(Longitude)) %>%
  st_as_sf(coords = c("Longitude", "Latitude"),  # make spatial layer using these columns
           remove = T, # don't remove these lat/lon cols from df
           crs = 4326)

# Need to join sites missing ecoregion information manually
benSampsStationsEco <- filter(benSampsStations1, is.na(US_L3CODE)) %>%
  st_intersection(dplyr::select(ecoregion4Large, US_L3CODE, US_L3NAME, US_L4CODE, US_L4NAME )) %>%
  mutate(US_L3CODE1 = as.character(`US_L3CODE.1`), US_L3NAME1 = as.character(`US_L3NAME.1`),
         US_L4CODE1 = as.character(`US_L4CODE.1`), US_L4NAME1 = as.character(`US_L4NAME.1`)) %>%
  dplyr::select(StationID, `Total Station Visits (Not Sample Reps)` = "Total.Station.Visits..Not.Sample.Reps.",
                US_L3CODE1, US_L3NAME1, US_L4CODE1, US_L4NAME1) %>%
  st_drop_geometry() # drop geometry for the join

# combine with benSampsStations with a join because for some reason rbind() is dropping the ecoregion information
benSampsStationsTogether <- left_join(benSampsStations1, benSampsStationsEco, 
                                      by = c('StationID', 'Total Station Visits (Not Sample Reps)')) %>%
  mutate(US_L3CODE = coalesce(US_L3CODE, US_L3CODE1), #ifelse(is.na(US_L3CODE), US_L3CODE1, US_L3CODE),
         US_L3NAME = coalesce(US_L3NAME, US_L3NAME1), #ifelse(is.na(US_L3NAME), US_L3NAME1, US_L3NAME),
         US_L4CODE = coalesce(US_L4CODE, US_L4CODE1), #ifelse(is.na(US_L4CODE), US_L4CODE1, US_L4CODE),
         US_L4NAME = coalesce(US_L4NAME, US_L4NAME1)) %>%  #ifelse(is.na(US_L4NAME), US_L4NAME1, US_L4NAME)) %>%
  dplyr::select( StationID, Sta_Desc, `Total Station Visits (Not Sample Reps)`, US_L3CODE, US_L3NAME, US_L4CODE, US_L4NAME)

benSampsStations <- st_intersection(benSampsStationsTogether, unrestrictedAssessmentRegionVAHU6Subbasin) %>% #assessmentRegionLarge) %>%
  rename('Total Station Visits (Not Sample Reps)' = "Total.Station.Visits..Not.Sample.Reps.") %>%
  distinct(StationID, .keep_all = T) %>% 
  dplyr::select(-c(OBJECTID:HUMOD, OBJECTID_1))

```



Calculate SCI for everyone

```{r sci helpers}
vmast <- masterTaxaGenus %>%
        # get Family level tolerance value, FFG
        rename('GenusTolVal' = 'TolVal',
               'TolVal' = 'FamTolVal',
               'GenusFFG' = 'FFG',
               'FFG' = 'FamFFG',
               'GenusHabit' = 'Habit',
               'Habit' = 'FamHabit') %>%
        mutate(e=ifelse(Order=="Ephemeroptera", 1, 0),
               p=ifelse(Order=="Plecoptera",1,0),
               t=ifelse(Order=="Trichoptera", 1, 0),
               tmin=ifelse((Order=="Trichoptera" & Family != "Hydropsychidae") | 
                             (Order=="Trichoptera" & is.na(Family)) , 1, 0), 
               ept=ifelse(e+p+t>0,1,0), 
               scraper = ifelse(FFG=="Scraper", 1, 0),
               chiro = ifelse(Family=="Chironomidae",1, 0),
               ptmin = ifelse(p + tmin > 0,1,0),
               `clinger-HS` = ifelse(Habit == 'Clinger' & ! Family %in% c("Hydropsychidae","Simuliidae"), 1, 0)) %>%
        # Then put it in long format so it can be merged to and input taxa list
        select(`Final VA Family ID`,TolVal, e,p,t, ept,ptmin, scraper, chiro,`clinger-HS`) %>% 
        distinct(`Final VA Family ID`, .keep_all = T) %>% # drop multiple rows bc working back to family level data from genus
        filter(!is.na(`Final VA Family ID`)) %>%
        pivot_longer(-`Final VA Family ID`, names_to = 'metric', values_to = 'metric_val') %>%
        #  pivot_longer(-`Final VA Family ID`, names_to = 'metric', values_to = 'metric_val') %>%
        filter(!is.na(metric_val))

### SCI calculation

SCI <- function(stationBenthicsDateRange, SCIchoice, benSamps, masterTaxaGenus, vmast){
  edas_options <- select(masterTaxaGenus, Class, Subclass, Order, Suborder, Superfamily, Family, `Final VA Family ID`, FinalID) %>%
    mutate(across(where(is.factor), as.character))
  edas_list <- select(edas_options, `Final VA Family ID`,FinalID)
  # for Excluding taxa, need a list of all Family level designations that may end up as a FinalID
  # these are all unique Family names and the few taxa that are the only 
  GenusNames <- c(unique(edas_options$FinalID)[!is.na(unique(edas_options$FinalID))])
  FamilyNames <- unique(edas_options$Family)[!is.na(unique(edas_options$Family))]
  SuperfamilyNames <- unique(edas_options$Superfamily)[!is.na(unique(edas_options$Superfamily))]
  SuborderNames <- unique(edas_options$Suborder)[!is.na(unique(edas_options$Suborder))]
  OrderNames <- unique(edas_options$Order)[!is.na(unique(edas_options$Order))]
  SubclassNames <- unique(edas_options$Subclass)[!is.na(unique(edas_options$Subclass))]
  ClassNames <- unique(edas_options$Class)[!is.na(unique(edas_options$Class))]
  
  
  EDASrare <- stationBenthicsDateRange %>%
    ########## #filter(str_detect(BenSampID, 'R110') & RepNum == 1) %>% # keep only rarified data and Rep1's
    mutate(Count = Individuals) %>% # Rename to match formatting of functions
    ######`Excluded Taxa` = ifelse(`Excluded Taxa` == T, -1, 0)) %>% 
    select(BenSampID, FinalID, Count, `Excluded Taxa`) %>%
    mutate(GenusTaxaLevel = ifelse(FinalID %in% GenusNames, T, F),
           FamilyTaxaLevel = ifelse(FinalID %in% FamilyNames, T, F),
           SuperfamilyTaxaLevel = ifelse(FinalID %in% SuperfamilyNames, T, F),
           SuborderTaxaLevel = ifelse(FinalID %in% SuborderNames, T, F),
           OrderTaxaLevel = ifelse(FinalID %in% OrderNames, T, F),
           SubclassTaxaLevel = ifelse(FinalID %in% SubclassNames, T, F),
           ClassTaxaLevel = ifelse(FinalID %in% ClassNames, T, F))
  
  # Work FinalID back up to Family Level
  EDASrare2 <- left_join(EDASrare,edas_list, by="FinalID") %>%
    filter(!is.na(`Final VA Family ID`)) %>%
    rename( `Genus Level Excluded Taxa` = `Excluded Taxa`)
  
  # We also need to do a little data manipulation to incorporate biologist exclusion information appropriately.
  exclusionMath  <- EDASrare2 %>%
    mutate(`Family Level Excluded Taxa` = 
             ifelse(`Genus Level Excluded Taxa` == -1, 
                    ifelse(`SuperfamilyTaxaLevel` == TRUE | `SuborderTaxaLevel` == TRUE | `OrderTaxaLevel` == TRUE | 
                             `SubclassTaxaLevel` == TRUE | `ClassTaxaLevel` == TRUE , -1, 0), 0 )) %>%
    # had to get super ifelse nesty here to make this logic work, ugly but works
    group_by(BenSampID, `Final VA Family ID`) %>%
    summarise(`Family Level Count` = sum(Count), 
              #`Genus Level Excluded Taxa` = sum(`Genus Level Excluded Taxa`),
              `Family Level Taxa` = n(),
              `Family Level Excluded Taxa` = sum(`Family Level Excluded Taxa`),
              `Final Family Level Taxa` = `Family Level Taxa` + sum(`Family Level Excluded Taxa`) )
  
  # Join bug traits
  bugTraits <- left_join(exclusionMath,vmast,by=c('Final VA Family ID') )
  
  
  if(SCIchoice == 'VSCI'){SCI <- VSCIcalculation(bugTraits,exclusionMath,vmast) %>%
    mutate(SCI = 'VSCI',
           `SCI Threshold` = 60) %>% 
    rename("SCI Score" ="Fam SCI")}
  if(SCIchoice == 'VCPMI63 + Chowan'){SCI <- VCPMI63calculation(bugTraits,exclusionMath,vmast) %>%
    mutate(SCI = 'VCPMI63 + Chowan',
           `SCI Threshold` = 40) %>% 
    rename("SCI Score" ="CPMI63+CHOWAN")}
  if(SCIchoice == 'VCPMI65 - Chowan'){SCI <- VCPMI65calculation(bugTraits,exclusionMath,vmast) %>%
    mutate(SCI = 'VCPMI65 - Chowan',
           `SCI Threshold` = 40) %>% 
    rename("SCI Score" ="CPMI65-CHOWAN")}
  
  SCI <- left_join(SCI, benSamps, by = 'BenSampID')
  
  return(SCI) 
}
```


Calculate VSCI for everyone

```{r vsci}
VSCIresults <- SCI(benthics, "VSCI", benSamps,  masterTaxaGenus, vmast) %>%
        mutate_if(is.numeric, round, digits=2) %>%# rounds all numeric columns to 2 decimal places
        arrange(`Collection Date`)
VSCIresults$Season <-  factor(VSCIresults$Season,levels=c("Spring","Outside Sample Window","Fall"))#,ordered=T)
```



Calculate VCPMI 63 for everyone

```{r vcpmi63}
VCPMI63results <- SCI(benthics, "VCPMI63 + Chowan", benSamps,  masterTaxaGenus, vmast) %>%
        mutate_if(is.numeric, round, digits=2) %>%# rounds all numeric columns to 2 decimal places
        arrange(`Collection Date`)
VCPMI63results$Season <-  factor(VCPMI63results$Season,levels=c("Spring","Outside Sample Window","Fall"))#,ordered=T)
```


Calculate VCPMI 65 for everyone

```{r vcpmi65}
VCPMI65results <- SCI(benthics, "VCPMI65 - Chowan", benSamps,  masterTaxaGenus, vmast) %>%
        mutate_if(is.numeric, round, digits=2) %>%# rounds all numeric columns to 2 decimal places
        arrange(`Collection Date`)
VCPMI65results$Season <-  factor(VCPMI65results$Season,levels=c("Spring","Outside Sample Window","Fall"))#,ordered=T)
```




Pin fresh data to board.

```{r pin to rsconnect}
pin(masterTaxaGenus, description = "Edas_Benthic_Master_Taxa_View from ODS", board = "rsconnect")
pin(benthics, description = "Edas_Benthic_View from ODS", board = "rsconnect")
pin(benSamps, description = "Edas_Benthic_Sample_View from ODS", board = "rsconnect")
pin(habSamps, description = "Edas_Habitat_Sample_View from ODS", board = "rsconnect")
pin(habValues, description = "Edas_Habitat_Values_View from ODS", board = "rsconnect")
pin(habObs, description = "Edas_Habitat_Observations_View from ODS", board = "rsconnect")
pin(totalHabitatScore, description = 'Calculated Total Habitat Score from ODS', board = 'rsconnect')
pin(benSampsStations, description = 'Unique Stations from BenSamps with sampling metrics, US Level 3 Ecoregion, and Assessment Region information', board = "rsconnect")

pin(VSCIresults, description = "VSCI results calculated from ODS_test", board = "rsconnect")
pin(VCPMI63results, description = "VCPMI63 + Chowan results calculated from ODS", board = "rsconnect")
pin(VCPMI65results, description = "VCPMI65 - Chowan results calculated from ODS", board = "rsconnect")

```



